This chapter will explain the concepts that were used in the creation of this pipeline, it will explain the theory that was used and how it all fits together.
% Literature Review
% \subsection{Literature Review}

\subsection{Mathematical Groundwork}
\subsubsection{Box Function}
The box function is a function defined as \\ 
\begin{center}
$\forall a,b \in \mathbb{R}, a \le b$\\
$
\Pi_{a,b}(x) 
=\begin{cases} 
      0 &  x < a \\
      1 & a \le x \le b \\
      0 & x > b \\
   \end{cases}$
\end{center}
This function is significant to the pipeline because it is the function that is used when the gridding algorithm is applied. The data that is obtained from the visibilities is placed onto a rectangular grid and this represents the box function.
\subsubsection{Fourier Transform}
The core of radio interferometry is Fourier theory, without it this pipeline would be infeasible and would not work. The most important aspect is the Fourier transform, this allows the pipeline to transform the signal we receive into data that it can make use of. The Fourier transform is a method of decompressing data into the frequencies that make it up. The function is given below.
\begin{center}
$\mathscr{F}\{f\}(s) = \int_{-\infty}^{+\infty}f(x)\,e^{-\imath 2\pi xs}dx$    
\end{center}
The inverse of the Fourier transform is the reverse process, it is a lossless inverse that will restore the data to its original form after it has been Fourier transformed already. The inverse is defined below.
\begin{center}
$\mathscr{F}^{-1}\{F\}(x) = \int_{-\infty}^{+\infty}F(s)\,e^{\imath 2\pi xs}ds$
\end{center}
The signals that are received from the radio interferometer are Fourier transforms of the sky. This means that the pipeline should be able to take the inverse Fourier transform and get data that it can use to create an image back.

\subsection{Positional Astronomy}
A geographical coordinate system is used to identify a position on the earth, but when one moves to an astronomical view one cannot use that system anymore. This section will explain the various systems that are used in celestial calculations.
\subsubsection{Equatorial Coordinates}
A coordinate system for the celestial view is needed in order to map the position of celestial objects. This is done by projecting the universe onto a sphere of arbitrary radius, this sphere is called the celestial sphere. The celestial equator is the projection of the equator onto this sphere. Every object in the universe has a fixed position on this sphere, except for the sun. This is because the earth orbits the sun. The path that the sun orbits the earth on is called the ecliptic\\ The North Celestial Pole(NCP) is the point obtained by projecting the north pole onto the celestial sphere, the South Celestial Pole(SCP) is obtained in a similar way. \\
We use a specific point on the celestial equator called the vernal equinox, this is the point where the celestial equator meets the ecliptic and it is the point from which we measure the location of all celestial objects. \\
The hour circle of an object is the circle on the celestial sphere that crosses the NCP and the object itself, while also perpendicularly intersecting with the celestial equator. 
\\
The right ascension $\alpha$, is the angular distance between the vernal equinox and the hour circle of the object along the celestial equator. It is measured in an Easterly direction. It is measured in Hours, Minutes and seconds.\\
The Declination $\delta$, is the angular distance from the celestial equator and along its hour circle. It is measured in Degrees, Arcmin, Arcsec.
\subsubsection{Hour Angle and Local Sidereal Time}
The Zenith is the position directly above the observer on the celestial sphere, and similarly the Nadir is the position directly below the observer on the celestial sphere. The local meridian is the hour circle that is formed when the NCP is connected with the Zenith. \\ 
The hour angle of a celestial object is the angular distance between the hour circle of a celestial object and the local meridian in a westerly direction. If the hour angle is the time till or since transit and can be used instead of right ascension to keep track of the stars as the move across the celestial sphere. \\
Local sidereal time is a time keeping system that keeps track of the stars, instead of keeping track of the sun, it keeps track of the vernal equinox. The local sidereal time is 4 minutes shorter than the system that keeps track of the sun, the normal solar day.
\subsubsection{Horizontal Coordinates}
In order to determine where a telescope should point on earth in order to observe a source with a specific hour angle, a different coordinate system is needed. The azimuth $\mathcal{A}$ and altitude $\mathcal{E}$ (elevation) is used by an observer on earth to locate an object in the observers sky, the observer's plane is known as the celestial horizon.The azimuth angle is measured in the celestial horizon from due north towards the east, while the altitude of a celestial object is the angle between it and the celestial horizon. Both azimuth and elevation is measured in degrees. The equations for converting between equatorial and horizontal coordinate systems are given below. \begin{eqnarray}
\cos\delta\cos H &=& \cos L_a\sin \mathcal{E} - \sin L_a\cos \mathcal{E}\cos \mathcal{A}\\
-\cos\delta\sin H&=& \cos \mathcal{E}\sin \mathcal{A}\\
\sin\delta &=& \sin L_a\sin \mathcal{E}+\cos L_a \cos \mathcal{E} \cos \mathcal{A} 
\end{eqnarray}
Where $L_a$ denotes latitude.
\subsubsection{Direction Cosine Coordinates}
This coordinate system allows the observer to define their own reference point on the celestial sphere, the point from which all other objects are measured, this reference point is known as the \textit{field center} or \textit{phase center}. \\
There are three coordinates in this system, \textit{\textbf{l}}, \textit{\textbf{m} }and\textit{ \textbf{n}}. The equations below are used to convert between the equatorial and direction cosine coordinate systems. 
\begin{eqnarray}
l &=&  \cos \delta  \sin \Delta \alpha \nonumber\\
m &=& \sin \delta \cos \delta_0 - \cos \delta \sin \delta_0 \cos\Delta \alpha \nonumber\\
\delta &=& \sin^{-1}(m\cos \delta_0 + \sin \delta_0\sqrt{1-l^2-m^2})\nonumber\\
\alpha &=& \alpha_0 + \tan^{-1}\bigg(\frac{l}{\cos\delta_0\sqrt{1-l^2-m^2}-m\sin\delta_0}\bigg)\nonumber
\end{eqnarray}
Where $\delta_0$ and $\alpha_0$ are the fundamental reference point of the telescope.
\subsection{Visibility Space}
\subsubsection{The Baseline}
The baseline is a separation vector between two antenna in an interferometric array, thus an array can consist of several baselines. The baseline is formed by subtracting the positions of one of the antenna in the array from the position of another antenna in the array. The baseline can be expressed as. \begin{equation}
\mathbf{b}_{\text{ENU}}
=
\lvert \mathbf{b} \rvert
\begin{bmatrix}
\sin \mathcal{A} \cos \mathcal{E}\\
\cos \mathcal{A} \cos \mathcal{E}\\
\sin \mathcal{E}
\end{bmatrix}
\end{equation}
In order to generalise the baseline a new system is needed to map the sky coordinates on the celestial sphere to the baseline. The \textbf{XYZ} system is used for this, this system is defined as follows.
\begin{itemize}
    \item The $X$-axis points towards $(H=0^\textrm{h}, \delta = 0^{\circ})$ 
    \item The $Y$-axis towards $(H=-6^\textrm{h}, \delta = 0^{\circ})$ 
    \item The $Z$-axis towards the NCP.
\end{itemize}
The XYZ coordinates can be calculated as such
\begin{equation}
\begin{bmatrix}
X\\Y\\Z
\end{bmatrix}=
\begin{bmatrix}
\lvert \mathbf{b} \rvert \cos \delta \cos H\\
-\lvert \mathbf{b} \rvert \cos \delta \sin H\\
\lvert \mathbf{b} \rvert \sin \delta
\end{bmatrix}
= \lvert \mathbf{b} \rvert
\begin{bmatrix}
\cos L_a \sin \mathcal{E} - \sin L_a \cos \mathcal{E} \cos \mathcal{A}\nonumber\\ 
\cos E \sin \mathcal{A} \nonumber\\
\sin L_a \sin \mathcal{E} + \cos L_a \cos \mathcal{E} \cos \mathcal{A}\\
\end{bmatrix}
\end{equation}
Where \textbf{b} is the amplitude of the baseline vector, H is the hour angle, $\delta$ is the Declination, $L_a$ is the latitude of the array.
\subsubsection{The u,v,w Space}
Now that the \textbf{XYZ} system is defined, the conversion to the \textit{u,v,w} system is possible. This system is defined below.
\begin{itemize}
    \item The $u$-axis lies in the celestial equatorial plane, and points toward the hour angle $H_0-6^\text{h}$.
    \item The $v$-axis lies in the plane of the great circle with hour angle $H_0$, and points toward the declination $\frac{\pi}{2}-\delta_0$.
    \item The $w$-axis points in the direction of $\mathbf{s_0}$.
\end{itemize}
The conversion from XYZ to uvw is defined as.
\begin{equation}
\begin{bmatrix}
u\\v\\w
\end{bmatrix}=
\begin{bmatrix}
\sin H_0 & \cos H_0 & 0\\ 
-\sin \delta_0 \cos H_0 & \sin\delta_0\sin H_0 & \cos\delta_0\\
\cos \delta_0 \cos H_0 & -\cos\delta_0\sin H_0 & \sin\delta_0\\
\end{bmatrix} 
\begin{bmatrix}
X\\Y\\Z
\end{bmatrix}
\end{equation}
\subsubsection{Visibilities}
The interferometer does not receive images of the sky, it receives a Fourier transform of the image of the sky. This Fourier transform is the visibility function.
Visibilities are what are received by the interferometer, each baseline receives a visibility and this visibility is used in conjunction with all the others in order to understand the shape of the visibility function and extract information about the sky. In short the visibility function is the Fourier transform of the sky that is received by the interferometer.
\subsubsection{UV Tracks and UV Coverage}
Over time, the position of the baseline changes as the earth rotates. This creates a path that is called the UV track of the baseline. If the UV tracks for each baseline are combined together, then the UV coverage is determined. The UV coverage is how much of the UV plane the interferometer is able to cover given its configuration. The visibilities from the baselines can be mapped to the UV tracks for the same baseline. 

\subsection{Imaging}
\subsubsection{Aliasing}\label{sec:Aliasing}
Aliasing is an effect that results in misidentification of signals and introduces distortion or errors. It is caused by a sampling rate that is not high enough to capture the signal properly\cite{aliasing}. The Nyquist Theorem is a theorem that is used to prevent aliasing, it states \textit{The sampling frequency should be at least twice the highest frequency contained in the signal.}\cite{aliasing} In radio interferometry, aliasing can cause the repetition of some signals, so a good sampling rate should always be chosen.

\subsubsection{Gridding}
Gridding is the process of placing the visibilities that have been read from the interferometer and placing them onto a grid based on the UV tracks of the baselines. The image is then created based off of this grid that has been created, the image is created by taking the inverse Fourier transform of the grid.\\
The image is two dimensional with $N_l \times N_m$ representing the size. Each pixel in the image has a cell size of $(\Delta \theta_l, \Delta \theta_m)$. In order to calculate the size of the image from the cell size, the following equation must be applied. $$N_l = \frac{\theta_l}{\Delta \theta_l}$$
$$N_m = \frac{\theta_m}{\Delta \theta_m}$$
Where,  $\Delta \theta_l\sim \Delta l$ , $\Delta \theta_m \sim \Delta m$, and $\Delta l = \cos{\Delta \theta_l}$, $\Delta m = \cos{\Delta \theta_m}$. The cell size that is chosen must satisfy the Nyquist theorem in order to avoid aliasing.\\
once the size of the grid has been determined, the visibilities must be placed onto the grid. This is done by convolving the visibilities along the sampling tracks with a function. This is then discretised onto regular points by using a shah function.\\
In order to get an image of the sky out of this grid, the inverse Fourier transform is applied, what is returned will be an image of the sky above the interferometer.

\subsubsection{Point Spread Function}
The Point Spread Function, PSF, sometimes referred to as the dirty beam, refers to the response of a
measurement system to a perfect point source.\cite{TEXTBOOK} The observed signal of an Interferometer is
actually the convolution of the true signal and the PSF, that is why when imaging is done, point sources
have distortion around them. As the PSF is the response of a measurement system to a perfect point source,
if a perfect point source were to be imaged, the PSF could clearly be seen for the interferometer that it
was applied to. The reason that the PSF exists is because unless the interferometer were able to observe the entire UV plane without gaps in the observation, when imaging is done, there will be errors, these errors come in the form of distortion via the PSF.
% Get articles form textbook 
